Road User video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda

### 2024-07-15 paper.qmd
Re-update table

tbl = d_all |>
  # NA is Unknown:
  mutate(mode = case_when(
    is.na(mode) ~ "unknown",
    TRUE ~ mode
  )) |>
  count(mode, sort = TRUE) |>
  mutate(percent_of_records = n / nrow(d_all)) |>
  mutate(percent_of_records = round(percent_of_records, 3) * 100) |>
  # Reclassify Unknown to unknown:
  arrange(desc(n)) |>
  rename_all(snakecase::to_title_case) |>
  # Rename N to "Number of records"
  rename(`Number` = N, `Percent` = `Percent of Records`) |>
  gt() |>
  gt_plt_bar_pct(column = `Percent`, fill = "#252525", scaled = TRUE, labels=TRUE, width=120, height=30, font_size = "15px") |> 
  cols_width(1 ~ px(400), 2 ~ px(80)) |> 
  tab_style(
    style = cell_text(size=px(18)),
    locations = cells_body(columns = Mode)
  ) |>
  gt_theme_espn()
tbl
# gt::gtsave(tbl, "tbl-mode.png")
knitr::include_graphics("tbl-mode.png")
```

@@

The cross-tabulation of reporting mode and offence type is shown in Table @tbl-mode-offences-crosstab, revealing some interesting tendencies.

>>>>

tbl = d_all |>
  # NA is Unknown:
  mutate(mode = case_when(
    is.na(mode) ~ "unknown",
    TRUE ~ mode
  )) |>
  count(mode, sort = TRUE) |>
  mutate(percent_of_records = n / nrow(d_all)) |>
  mutate(percent_of_records = round(percent_of_records, 3) * 100) |>
  # Reclassify Unknown to unknown:
  arrange(desc(n)) |>
  rename_all(snakecase::to_title_case) |>
  # Rename N to "Number of records"
  rename(`Number` = N, `Percent` = `Percent of Records`) |>
  gt() |>
  gt_plt_bar_pct(column = `Percent`, fill = "#252525", scaled = TRUE, labels=TRUE, width=120, height=30, font_size = "15px") |> 
  cols_width(1 ~ px(400), 2 ~ px(80)) |> 
  tab_style(
    style = cell_text(size=px(18)),
    locations = cells_body(columns = Mode)
  ) |>
  gt_theme_espn()
# tbl
# gt::gtsave(tbl, "tbl-mode.png")
knitr::include_graphics("tbl-mode.png")
```

@@

The cross-tabulation of reporting mode and offence type is shown in @tbl-mode-offences-crosstab, revealing some interesting tendencies.
